decompr: GVC decomposition in R

### 2015-02-01 draft.Rnw
Update draft.Rnw
Starting with conclusion

>>>>

GVCs describe the increasingly international organization of production structures.
As more and more regional trade agreements come into force, 
which drive down trade costs and harmonize product standards,
it becomes more and more attractive for firms to outsource certain tasks of their production lines.
Research on international trade analysing this development evolves quickly and reveals important implications of GVCs for economic growth and competitiveness.  
\textbf{decompr} aims at facilitating this reasearch by simplifying the calculation of standard GVC indicators.
The purpose is to accelerate the research and, especially, to make it accesible to a wider audience.
